PANCHANGE_variable_creation

### 2020-11-03 PANCHANGE_variable_creation.Rmd
Added binary variable for if the participant signed up 3/6/9 month prior to pandemic

Creating variables for subset of participants dependent on when they signed up to GLAD (prepan)
```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
# Date of 3 months prior to the 1st of March
date_3months_prior_march_1st <- as.POSIXct("2019-12-01")

@@

>>>>

Creating date variables for subset of participants dependent on when they signed up to GLAD (prepan)
```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
# Date of 3 months prior to the 1st of March
date_3months_prior_march_1st <- as.POSIXct("2019-12-01")

@@

```{r subset of participants who signed up in 3 months prior to pandemic}
dat <- dat %>%
  mutate(
    prepandemic_3_months_numeric =
      if_else(
        startDate.prepandemic > date_3months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
        prepandemic_march_1_numeric == 1, #signed up before March 1st 
        true = 0, # Participant signed up after December 1st 
        false = 1, # Participant signed up before December 1st
        missing = NA_real_
      )
  )

dat <- dat %>%
  mutate(
    prepandemic_3_months =
      recode_factor(
        prepandemic_3_months_numeric,
        "0" = "Sign up after 01 December",
        "1" = "Sign up before 01 December"
      )
  )

dat %>%
  freq(prepandemic_3_months)
```

```{r subset of participants who signed up in 6 months prior to pandemic}
dat <- dat %>%
  mutate(
    prepandemic_6_months_numeric =
      if_else(
        startDate.prepandemic > date_6months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
        prepandemic_march_1_numeric == 1,
        true = 0, # Participant signed up after September 1st 
        false = 1, # Participant signed up before September 1st
        missing = NA_real_
      )
  )

dat <- dat %>%
  mutate(
    prepandemic_6_months =
      recode_factor(
        prepandemic_6_months_numeric,
        "0" = "Sign up after 01 September",
        "1" = "Sign up before 01 September"
      )
  )

dat %>%
  freq(prepandemic_6_months)
```

```{r subset of participants who signed up in 9 months prior to pandemic}
dat <- dat %>%
  mutate(
    prepandemic_9_months_numeric =
      if_else(
        startDate.prepandemic > date_9months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
        prepandemic_march_1_numeric == 1,
        true = 0, # Participant signed up after June 1st 
        false = 1, # Participant signed up before June 1st
        missing = NA_real_
      )
  )

dat <- dat %>%
  mutate(
    prepandemic_9_months =
      recode_factor(
        prepandemic_9_months_numeric,
        "0" = "Sign up after 01 June",
        "1" = "Sign up before 01 June"
      )
  )

dat %>%
  freq(prepandemic_9_months)
```
